The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step

### 2017-03-29 Moving temporal window - HESS/template.tex
HESS paper under work.

		The impact of the MTW on prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24h totals at 6h time steps. The prediction skill was found to have improved by the MTW, and even to a greater extent after recalibrating the AM parameters. Moreover, the improvement was greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the meteorological archive.

		However, in order to produce quantitative precipitation predictions the MTW requires sub-daily precipitation time series, which are generally available for a shorter period than daily precipitation archives. Therefore, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW. The assessed approaches were not successful, emphasizing the need to use time series with an appropriate chronology. These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data at sub-daily time step.

>>>>

		The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24h totals at 12h, 6h, and 3h time steps. The prediction skill was found to have improved by the MTW, as well as the reliability of the prediction. Moreover, the improvements were greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the meteorological archive.

		Both improvements of the analogy criterion and the performance scores were found to be higher for MTWs with a smaller time step (3h). A 3h-MTW provides 8 times more candidate situations, even though not fully independent. As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive. The technique being very simple and easily applicable, it should be considered for several applications in different contexts, may it be for operational forecasting or climate-related studies.
